{\em Cloudbreak}: Accurate and Scalable Genomic Structural Variation Detection in the Cloud with MapReduce

### 2014-01-13 manuscript/bioinfo/document.tex
update tables

\begin{table*}[b]
\begin{center}
%\resizebox{\textwidth}{!}{
\footnotesize
\begin{tabular}{r|rrr|rrrrr}
  \cline{2-9}
   &                     & Prec. & Recall & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
\hline
\multirow{7}{*}{\begin{sideways}Deletions\end{sideways}} & Total Number &          &           & 224 &  84 & 82 &  31 & 26\\ 
  \hline
\cline{2-9}
&  Cloudbreak    &  0.638 & \textbf{0.678} & \textbf{153} (9)  & 61 (0) &  62 (0) & 12 (0) & 15 (0) \\ 
&  BreakDancer   &  0.356 & 0.49 & 89 (0)  & 54 (0) &  53 (0) & 8 (0) & 15 (0) \\ 
&  GASVPro        & 0.146 & 0.432 & 83 (2)  & 32 (0) &  55 (0) & 8 (0) & 15 (0) \\ 
&  DELLY-RP           & 0.457 & 0.613 & 114 (3)  & \textbf{68} (0) &  \textbf{66} (0) & 9 (1) & 17 (0) \\ 
&  DELLY-SR           & \textbf{0.679} & 0.166 & 0 (0)  & 3 (0) &  49 (0) & 6 (0) & 16 (0) \\ 
&  Pindel           & 0.462 & 0.421 & 96 (\textbf{11})  & 24 (0) &  48 (0) & 5 (0) & 15 (0)\\ 
&  MoDIL           & 0.132  & 0.66 & 123 (6)  & 66 (\textbf{3}) &  \textbf{66} (\textbf{11}) & \textbf{17} (\textbf{7}) & \textbf{23} (\textbf{8})\\ 
   \hline
\multirow{5}{*}{\begin{sideways}Insertions\end{sideways}} & Total Number &          &           & 199 &  83 & 79 &  21 & 21\\ 
\cline{2-9}
&  Cloudbreak   &0.451 & \textbf{0.305}  & \textbf{79} (\textbf{32})  & \textbf{32} (\textbf{18}) &  \textbf{11} (8) & 1 (0) & 0 (0) \\ 
&  BreakDancer & 0.262 & 0.0968  & 23 (5)  & 14 (5) &  2 (1) & 0 (0) & 0 (0) \\ 
&  Pindel          & \textbf{0.572} & 0.196 & 52 (25)  & 5 (1) &  10 (\textbf{9}) & \textbf{3} (\textbf{2}) & \textbf{9} (\textbf{9})\\ 
&  MoDIL          & 0.186 & 0.0521 & 14 (1)  & 4 (0) &  1 (0) & 2 (\textbf{2}) & 0 (0)\\ 
\hline
\end{tabular}
%}
\end{center}
\caption{The number of simulated deletions and insertions in the 30X diploid chromosome 2 with Venter indels found by each tool at maximum sensitivity, as well as the number of those variants that were discovered exclusively by each tool (in parentheses). The total number of variants in each size class in the true set of deletions and insertions is shown in the first row of each section.}
\label{chr2DeletionAndInsertionPredsMaxSensitivity}
\end{table*}

@@

\begin{table*}
\begin{center}
%\resizebox{\textwidth}{!}{
\footnotesize
\begin{tabular}{r|rrr|rrrrr}
  \cline{2-9}
&  & Prec. & Recall & 40-100bp & 101-250bp & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
\hline
\multirow{6}{*}{\begin{sideways}Deletions\end{sideways}} & Total Number & & & 7,462 & 240 & 232 & 147 & 540 \\
  \hline
\cline{2-9}
& Cloudbreak & 0.0943 & \textbf{0.17} & \textbf{573} (\textbf{277})  & \textbf{176} (\textbf{30}) &  \textbf{197} (\textbf{18}) & \textbf{121} (\textbf{6}) & \textbf{399} (\textbf{24}) \\ 
& BreakDancer & 0.137 & 0.123 & 261 (29)  & 136 (3) &  178 (0) & 114 (0) & 371 (0) \\  
&  GASVPro & 0.147 & 0.0474 & 120 (21)  & 40 (2) &  85 (0) & 36 (0) & 128 (0) \\ 
&  DELLY-RP & 0.0931 & 0.1 & 143 (6)  & 128 (3) &  167 (1) & 103 (0) & 323 (1) \\ 
&  DELLY-SR & 0.153 & 0.0485 & 0 (0)  & 26 (0) &  123 (0) & 66 (0) & 203 (0) \\ 
&  Pindel & \textbf{0.179} & 0.0748 & 149 (8)  & 61 (0) &  149 (0) & 69 (1) & 217 (0) \\ 
\hline
\multirow{4}{*}{\begin{sideways}Insertions\end{sideways}} & Total Number & & & 536 & 114 & 45 & 1 & 0 \\
\cline{2-9}
& Cloudbreak & 0.0323 & \textbf{0.455} & \textbf{265} (\textbf{104})  & \textbf{49} (\textbf{24}) &  3 (1) & 0 (0)  & 0 (0)  \\ 
& BreakDancer & 0.0281 & 0.181 & 97 (10)  & 27 (5) &  2 (1) & 0 (0) & 0 (0) \\  
&  Pindel & \textbf{0.0387} & 0.239 & 144 (45)  & 14 (7) &  \textbf{7} (\textbf{6}) & \textbf{1} (\textbf{1}) &  0 (0) \\ 
\hline
\end{tabular}
%}
\end{center}
\caption{The precision and recall with respect to the gold standard set of deletions and insertions for each tool on the NA18507 data, as well as the number of variants found in each size class found. Exclusive predictions are in parentheses. For deletions, the same cutoffs were used as for the simulated data as in Supplementary Table \ref{Schr2DeletionPredsFDR10}, adjusted for the difference in coverage from 30X to 37X. For insertions, the maximum sensitivity cutoff was used.}
\label{NA18507DeletionAndInsertionPreds}
\end{table*}

>>>>

\begin{table*}[b]
\begin{center}
%\resizebox{\textwidth}{!}{
\footnotesize
\begin{tabular}{r|rrrr|rrrrr}
  \cline{2-10}
   &                     & Prec. & Recall & F1 & 40-100bp  & 101-250bp  & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
\hline
\multirow{7}{*}{\begin{sideways}Deletions\end{sideways}} & Total Number &          &           &  &  224 &  84 & 82 &  31 & 26\\ 
  \hline
\cline{2-10}
&  Cloudbreak    &  0.638 & \textbf{0.678} & \textbf{0.657} & \textbf{153} (9)  & 61 (0) &  62 (0) & 12 (0) & 15 (0) \\ 
&  BreakDancer   &  0.356 & 0.49 & 0.412 & 89 (0)  & 54 (0) &  53 (0) & 8 (0) & 15 (0) \\ 
&  GASVPro        & 0.146 & 0.432 & 0.218 & 83 (2)  & 32 (0) &  55 (0) & 8 (0) & 15 (0) \\ 
&  DELLY-RP           & 0.457 & 0.613 & 0.613 & 114 (3)  & \textbf{68} (0) &  \textbf{66} (0) & 9 (1) & 17 (0) \\ 
&  DELLY-SR           & \textbf{0.679} & 0.166 &  0.266 & 0 (0)  & 3 (0) &  49 (0) & 6 (0) & 16 (0) \\ 
&  Pindel           & 0.462 & 0.421 &  0.44 & 96 (\textbf{11})  & 24 (0) &  48 (0) & 5 (0) & 15 (0)\\ 
&  MoDIL           & 0.132  & 0.66 & 0.22 & 123 (6)  & 66 (\textbf{3}) &  \textbf{66} (\textbf{11}) & \textbf{17} (\textbf{7}) & \textbf{23} (\textbf{8})\\ 
   \hline
\multirow{5}{*}{\begin{sideways}Insertions\end{sideways}} & Total Number &          &           & & 199 &  83 & 79 &  21 & 21\\ 
\cline{2-10}
&  Cloudbreak   &0.451 & \textbf{0.305}  & \textbf{0.364}  & \textbf{79} (\textbf{32})  & \textbf{32} (\textbf{18}) &  \textbf{11} (8) & 1 (0) & 0 (0) \\ 
&  BreakDancer & 0.262 & 0.0968  & 0.141  & 23 (5)  & 14 (5) &  2 (1) & 0 (0) & 0 (0) \\ 
&  Pindel          & \textbf{0.572} & 0.196 &  0.292 & 52 (25)  & 5 (1) &  10 (\textbf{9}) & \textbf{3} (\textbf{2}) & \textbf{9} (\textbf{9})\\ 
&  MoDIL          & 0.186 & 0.0521 &  0.0814 & 14 (1)  & 4 (0) &  1 (0) & 2 (\textbf{2}) & 0 (0)\\ 
\hline
\end{tabular}
%}
\end{center}
\caption{The number of simulated deletions and insertions in the 30X diploid chromosome 2 with Venter indels found by each tool at maximum sensitivity, as well as the number of those variants that were discovered exclusively by each tool (in parentheses). The total number of variants in each size class in the true set of deletions and insertions is shown in the first row of each section.}
\label{chr2DeletionAndInsertionPredsMaxSensitivity}
\end{table*}

@@

\begin{table*}
\begin{center}
%\resizebox{\textwidth}{!}{
\footnotesize
\begin{tabular}{r|rrrr|rrrrr}
  \cline{2-10}
&  & Prec. & Recall & F1 & 40-100bp & 101-250bp & 251-500bp & 501-1000bp & $>$ 1000bp \\ 
\hline
\multirow{6}{*}{\begin{sideways}Deletions\end{sideways}} & Total Number & & & & 7,462 & 240 & 232 & 147 & 540 \\
  \hline
\cline{2-10}
& Cloudbreak & 0.0943 & \textbf{0.17} & 0.121 & \textbf{573} (\textbf{277})  & \textbf{176} (\textbf{30}) &  \textbf{197} (\textbf{18}) & \textbf{121} (\textbf{6}) & \textbf{399} (\textbf{24}) \\ 
& BreakDancer & 0.137 & 0.123 &  \textbf{0.13} & 261 (29)  & 136 (3) &  178 (0) & 114 (0) & 371 (0) \\  
&  GASVPro & 0.147 & 0.0474 &  0.0717 & 120 (21)  & 40 (2) &  85 (0) & 36 (0) & 128 (0) \\ 
&  DELLY-RP & 0.0931 & 0.1 &  0.0965 & 143 (6)  & 128 (3) &  167 (1) & 103 (0) & 323 (1) \\ 
&  DELLY-SR & 0.153 & 0.0485 &  0.0736 & 0 (0)  & 26 (0) &  123 (0) & 66 (0) & 203 (0) \\ 
&  Pindel & \textbf{0.179} & 0.0748 &  0.106 & 149 (8)  & 61 (0) &  149 (0) & 69 (1) & 217 (0) \\ 
\hline
\multirow{4}{*}{\begin{sideways}Insertions\end{sideways}} & Total Number & & & & 536 & 114 & 45 & 1 & 0 \\
\cline{2-10}
& Cloudbreak & 0.0323 & \textbf{0.455} &  0.0604 & \textbf{265} (\textbf{104})  & \textbf{49} (\textbf{24}) &  3 (1) & 0 (0)  & 0 (0)  \\ 
& BreakDancer & 0.0281 & 0.181 &  0.0487 & 97 (10)  & 27 (5) &  2 (1) & 0 (0) & 0 (0) \\  
&  Pindel & \textbf{0.0387} & 0.239 &  \textbf{0.0666} & 144 (45)  & 14 (7) &  \textbf{7} (\textbf{6}) & \textbf{1} (\textbf{1}) &  0 (0) \\ 
\hline
\end{tabular}
%}
\end{center}
\caption{The precision and recall with respect to the gold standard set of deletions and insertions for each tool on the NA18507 data, as well as the number of variants found in each size class found. Exclusive predictions are in parentheses. For deletions, the same cutoffs were used as for the simulated data as in Supplementary Table \ref{Schr2DeletionPredsFDR10}, adjusted for the difference in coverage from 30X to 37X. For insertions, the maximum sensitivity cutoff was used.}
\label{NA18507DeletionAndInsertionPreds}
\end{table*}
